\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-25 paper/examples.tex
paper: minor fix

\todo{fill in the XX values}
Before she can perform her queries, the researcher must develop a strategy
for handling the missing values. She currently has two options:
1) she could drop records with missing values in relevant fields,
2) she could use a standard data imputation package on all of her data. Both of these
approaches have significant drawbacks. For the query pictured in 
Fig.~\ref{fig:example-query}, (1) drops XXXX percent of the relevant tuples,
while her previous experiences with (2) have proven be expensive. In a previous project, she
worked with the American Community Survey data (671,153 rows), and performing imputation on the whole
dataset took XXX hours. The analyst needs a more complete picture
of the data, so (1) is insufficient, and she is under time pressure, so (2)
is infeasible.

>>>>

Before she can perform her queries, the researcher must develop a strategy
for handling the missing values. She currently has two options:
1) she could drop records with missing values in relevant fields,
2) she could use a standard data imputation package on all of her data. Both of these
approaches have significant drawbacks. For the query pictured in 
Fig.~\ref{fig:example-query}, (1) drops 1492 potentially relevant tuples,
while her previous experiences with (2) have proven be expensive. In a previous project, she
worked with the American Community Survey data (671,153 rows), and performing imputation on the whole
dataset took \todo{XXX hours}. The analyst needs a more complete picture
of the data, so (1) is insufficient, and she is under time pressure, so (2)
is infeasible.
